Solving smooth system of algebraic equations

### 2021-06-17 article/lipshitz.tex
work on article

\begin{lemm}
  Let $Ω$ be a compact set in a Banach space with a norm $\|.\|$.  Let $f$ be a
  function in $]0,1] × Ω → Ω$. We assume that $f$ is $(L,α)$-Lipschitz for
  some $L > 0$ and $α ≥ 0$ which we define by:

  \begin{enumerate}
  \item $f$ is continuous and bounded on $]0,1] × Ω$,
  \item $∀t ∈ ]0,1], ∀x,y ∈ Ω, \|f(t,y) - f(t,x)\| ≤ \frac{L}{tᵅ} \|y - x\|$ and
  \end{enumerate}

  Then, the differential equation
  \begin{eqnarray}
    x'(t) = f(t,x(t)) \label{lipschitz-diffeq}
  \end{eqnarray}
  has unique maximal
  solution defined for $t ∈ [0,1]$ for any initial condition $x(t₀) = x₀ ∈ Ω$
  with $t₀ ∈ [0,1]$. This solutions are of class ${\cal C}¹$
\end{lemm}

@@

This proves by the standard Cauchy-Lipschitz result that for any initial condition
$x(t₀) = x₀ ∈ Ω$ with $t₀ ∈ ]0,1]$, we have a unique solution on $[t,1]$ for
        any $0 < t < t₀$ and therefore a unique solution in $]0,1]$. Then, as
            $f$ is bounded on $[0,1] × Ω$ and by compacity $x(t)$ and $x'(t)$
            both admit a limit in $t = 0$ and the limit of the latter is the
            derivative of $x$ in $0$ by
            the usual result on the limit of derivatives.

@@

We define $n₁(t) = t^{2L}$ and $n_α(t) = e^{-\frac{2L}{α-1} t^{1-α}}$ when $α ≥
0$ and $α ≠ 1$.
In all cases, we have  $n'_α(t) = \frac{2L}{tᵅ} n_α(t)$. Indeed:
\begin{itemize}
\item For $α = 1$, $n'₁(t) = 2L t^{2L-1} = \frac{2L}{t} n₁(t)$
\item For $α > 0, α≠ 1$, $n'_α(t) = 2L t^{-α} e^{- \frac{2L}{α-1} t^{1-α}} = \frac{2L}{tᵅ} n_α(t)$
\end{itemize}

Then, we define the
following norms on the set of continuous functions from $[0,1]$ to $Ω$:
$$\|x\|_α = \max_{t ∈ ]0,1]} \frac{\|x(t)\|}{n_α(t)}$$

@@

We assume that the initial condition of the differential equation
\ref{lipschitz-diffeq} is
$x(0) = x₀ ∈ Ω$.
We define the following operator on continuous function from $[0,1]$ to
$Ω$:
$$F(x) = x₀ + ∫^t_0 f(u,x(u)).{\rm d} u$$

For ant $t ∈ ]0,1]$, we have:
\begin{eqnarray*}
  \|F(y)(t) - F(x)(t)\| &≤& ∫^t_0 \|f(u,y(u)) - f(u,x(u))\| {\rm d} u \cr
  &≤& ∫^t_0 \frac{L}{uᵅ} \|y(u) - x(u)\| {\rm d} u \cr
  &≤& \|y - x\|_α ∫^t_0 \frac{L}{uᵅ} n_α(u)  {\rm d} u \cr
  &≤& \|y - x\|_α ∫^t_0 \frac{1}{2} n'_α(u)  {\rm d} u \cr
  &≤&\frac{1}{2} \|y - x\|_α n_α(t) \cr
\|F(y) - F(x)\|_α &≤& \frac{1}{2} \|y - x\|_α
\end{eqnarray*}

>>>>

\begin{lemm}
  Let $Ω$ be an open set of $\SNR$ for the topology of the sphere.
  Let $f$ be a
  function in $]0,1] × Ω → ℝ^{n+1}$ such that $f(t,x)$ is tangent to $\SNR$ at $x$. We assume that $f$ is $(L,α)$-Lipschitz for
  some $L > 0$ and $α ≥ 0$ which we define by:

  \begin{enumerate}
  \item $f$ is continuous and bounded on $]0,1] × Ω$,
  \item $∀t ∈ ]0,1], ∀x,y ∈ Ω, \|f(t,x) - f(t,y)\| ≤ \frac{L}{tᵅ} \|x - y\|$ and
  \end{enumerate}

  Then, the differential equation
  \begin{eqnarray}
    x'(t) = f(t,x(t)) \label{lipschitz-diffeq}
  \end{eqnarray}
  has unique maximal for any initial condition $x(t₀) = x₀ ∈ Ω$
  with $t₀ ∈ [0,1]$. This solutions are of class ${\cal C}¹$.

  Moreover, if we can prove that a solution can't converge to a point outside
  $Ψ$, then this solution is total, i.e. defined on $[0,1]$.
\end{lemm}

@@

This proves by the standard Cauchy-Lipschitz result that for any initial condition
$x(t₀) = x₀ ∈ Ω$ with $t₀ ∈ ]0,1]$, we have a unique solution on $[t,1]$ for
    any $0 < t < t₀$ and therefore a unique maximal solution.

    It remains to show that the solution is of class ${\cal C}¹$ even in $0$.
    If a maximal solution is defined on $]0,b]$, then by compacity and because
        $f(t,x)$ is bounded, both $x(t)$ and $x'(t)$ have limits for $t=0$ (this
        limit may be outside of $Ψ$).  The limit of the latter is the derivative
        of $x$ in $0$ by the usual result on the limit of derivatives.
        We do not have that $x'(0) = f(0,x(0))$ as $f$ is not even defined in $0$.

@@

We define $n₁(t) = t^{2L}$ and $n_α(t) = e^{-\frac{2L}{α-1} t^{1-α}}$ when $α >
1$. In all cases, we have $n(t) → 0$ when $t → 0$ and $n'_α(t) = \frac{2L}{tᵅ}
n_α(t)$. Indeed:
\begin{itemize}
\item For $α = 1$, $n'₁(t) = 2L t^{2L-1} = \frac{2L}{t} n₁(t)$
\item For $α ≥ 0, α≠ 1$, $n'_α(t) = 2L t^{-α} e^{- \frac{2L}{α-1} t^{1-α}} = \frac{2L}{tᵅ} n_α(t)$
\end{itemize}

Then, we define the
following norms on the set of continuous, partial functions from $[0,1]$ to $Ω$:
$$\|x\|_α = \max_{t ∈ ]
0,1], x(t) \rm defined} \frac{\|x(t)\|}{n_α(t)}$$

@@

We assume that the initial condition of the differential equation
\ref{lipschitz-diffeq} is
$x(0) = x₀ ∈ Ω$.
We define the following operator on continuous partial function from $[0,1]$ to
$Ω$:
$$F(x)(t) = x₀ + ∫^t_0 f(u,x(u)).{\rm d} u$$

For any $t ∈ ]0,1]$, we have:
\begin{eqnarray*}
  \|F(x)(t) - F(y)(t)\| &≤& ∫^t_0 \|f(u,x(u)) - f(u,y(u))\| {\rm d} u \cr
  &≤& ∫^t_0 \frac{L}{uᵅ} \|x(u) - y(u)\| {\rm d} u \cr
  &≤& \|x - y\|_α ∫^t_0 \frac{L}{uᵅ} n_α(u)  {\rm d} u \cr
  &≤& \|x - y\|_α ∫^t_0 \frac{1}{2} n'_α(u)  {\rm d} u \cr
  &≤&\frac{1}{2} \|x - y\|_α n_α(t) \cr
\|F(x) - F(y)\|_α &≤& \frac{1}{2} \|x - y\|_α
\end{eqnarray*}
